Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-17 doc/manuscript/manuscript.Rmd
update methods.

 <!-- Preceeding the steps in that, we grew the isolate(s) on PDA, and transferred plugs to Potato Dextrose Broth. We grew the culture in broth until there was significant mycelial growth, but before the mycelial mat became 'solid' (about 4-5 days).  We collected the mycelia using a buchner funnel, removed the agar plugs, lyophilized the mycelia, then pulverized it by hand in whirl-pak bags.  The lyophilized mycelia was then used in the procedure as printed. Lyophilzed mycelia was stored in microcentrifuge tubes in the -20 freezer until needed for extractions.  -->

Prior to DNA extraction, isolates were grown on PDA and plugs were subsequently transferred to Potato Dextrose Broth (PDB) where they were grown until there was significant mycelial growth, but before the mycelial mat became solidified (4--5 days).
Mycelial was collected in a buchner funnel, agar plugs removed, lyophilizedm and pulverized manually in whirl-pak bags. 
Lyophilized mycelia was then stored in microcentrifuge tubes at -$20^{\circ}$C until needed for DNA extraction.

DNA was purified using a phenol-chloroform extraction method.
First, approximately 25 mg of lyophilized mycelia was suspended in 600$\mu$l of LETS Buffer (0.1 M LiCl, 0.01 M Na2EDTA, 0.01 M Tris-Cl (pH 7.4), 0.2% SDS) in a 2.0ml microcentrifuge tube.
An equal amount of buffer-saturated phenol (600$\mu$l) was added and mixed by inversion, followed by 300$\mu$l chloroform, mixed by inversion. 
The suspension was then transferred into a 2.0ml Phase-lock gel tube (VWR, Randor, PA) and centrifuged for 8--10 minutes at 12,000 RPM.
Another aloquat of 300$\mu$l was added and centrifuged for another 8--10 minutes at 12,000 RPM and the aqueous phase was subsequently transferred into a microcentrifuge tube with an equal volume of 2-propanol added and mixed via gentle inversion.

<!-- using a Qiagen DNeasy Plant Mini Kit (Qiagen Inc., Valencia, CA) according to the manufacturer's instructions. -->

<!-- Fungal DNA mini-prep Updated from Jeff Rollins’ protocol           Rev. Nov 2012

Sclerotinia spp. Phenol/Chloroform extraction-

1) Spin 2.0 ml Phase-lock gel microcentrifuge tubes @14,000 rpm for 30 sec.- 2 for each sample to be extracted

2) Place 600 ul LETS buffer in 2.0 ml microcentrifuge (round-bottomed)  tube

3) Add ~25 mg of lyophilized mycelia; mix by inverting (shaking, flicking) tube.

4) Add an equal volume (600ul) of buffer-saturated Phenol.  Invert to mix.

5) Add 300ul chloroform to tubes- invert to mix.

6) Pour suspension into Phase-lock  gel tubes.

7) Spin Phase-lock tubes @12,000 RPM for 8-10 min. to separate phases.

8) Add another volume (300ul per tube) of chloroform, invert gently to mix.  
    Spin again @ 12,000 RPM for 8 min.

9) Pour off top (aqueous) layer into micro-centrifuge tube.

10) Add an equal volume 2-propanol to volume in each tube.  Mix by gently inverting. Nucleic acids will be visible as transluscent strands in tubes.  
(Optional- Place in freezer (-20OC) overnight.)

**Turn on heat block to ‘low’ setting**

11) Spin tubes @ 12,000 RPM for 14 min.  White or loose semi-translucent pellets should be visible in tube.

12) Rinse pellet with ice-cold 70% EtOH, pouring off alcohol carefully- watch out for ‘loose’ pellets (re-spin if necessary).  Invert on paper towel for ~ 20 min to dry.

13) Resuspend pellet in 450 ul TE, then add 10 ul RNAase to each tube- invert or flick to dissolve pellet.  Incubate tubes on heat block at 37OC for 30 min.

14) Add 450 ul Phenol to each tube.  Invert tubes to mix.

16) Add 450 ul chloroform to each tube, invert to mix.

15) Transfer tube contents to Phase-lock  tubes, then spin @ 14,000 RPM for 10 min. to separate phases

16) Add 300 ul chloroform to each tube, invert to mix.

17) Spin @ 14,000 RPM for 8-10 min. to again separate phases.

18) Using wide-bore pipette tip, transfer aqueous phase to 1.5 micro-centrifuge tube- recover up to 450ul (not more) to keep total volume within capacity of micro-centrifuge tube.

19) Add 0.1 volume (45ul) 3M NaOAc to each tube.  Add two volumes ice-cold absolute EtOH (fill tube).  Incubate on ice for 30 min.- translucent material should be visible in tubes.
(Optional- Place in freezer (-20OC) overnight.)

20) Centrifuge at 14,000 RPM for 10 min.

21) Pour off EtOH, being careful not to dislodge pellet.  Rinse in cold 70% EtOH, then dry pellet on paper towels for at least 15 min.  Pellets may appear as white “pellets” in bottom of tube, or may appear as translucent smears on side of tube.

22) Resuspend pellets in 200ul TE.  (Place in 4OC refrig for ~24 hrs to allow pellet to rehydrate). -->

>>>>

Prior to DNA extraction, isolates were grown on PDA and plugs were subsequently transferred to Potato Dextrose Broth (PDB) where they were grown until there was significant mycelial growth, but before the mycelial mat became solidified (4--5 days).
Mycelial was collected in a buchner funnel, agar plugs removed, lyophilized and pulverized manually in whirl-pak bags. 
Lyophilized mycelia was then stored in microcentrifuge tubes at -$20^{\circ}$C until needed for DNA extraction.
DNA from 25mg of pulverized mycelia was purified using a phenol-chloroform extraction method followed by alcohol precipitation, suspending the DNA in 200$\mu$l TE [@sambrook1989molecular].
Suspended DNA was stored at $4^{\circ}$C until genotyping.
